Autonomous Quadrotor Landing on a Moving Platform

### 2016-04-18 docs/report/report.tex
more updates to report

\section{Introduction}
The idea of quadrotor has been explored by several companies and researchers since quadrotors became a popular alternative to fixed wing and single rotor aircraft (DJI auto landing, Pixhawk, make a reference). However most of these methods usually assume that the landing zone is static and that there is very little wind or disturbances. In cases of high wind or a rapidly moving platform, which from the quadrotor's reference frame can be be though of as nearly equivalent cases, normal autonomous landing procedures will likely fail.

Over the years there has been been at least some interest in the problem of landing a quadrotor on a moving platform and there have been at least 5 academic publications on the topic \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012}. The problem has been explored from a fairly wide range of approaches.

@@

\section{Related Work}
The challenging of autonomous landing can be categorized into three distinct parts. First, the quadrotor must sense or detect the landing target to obtain positional estimates relative to the quadrotor. Secondly, the quadrotor must plan its rendezvous trajectory with the landing target. Third and finally, the quadrotor must apply a set of controller commands to approach the platform, matching both speed and heading on the approach and land on the moving target.

\subsection{Perception and State Estimation}
For perception existing solutions use a variety of simple to complex techniques. In \cite{Kim2014} a basic color threshold technique was to identify the landing target, while \cite{Herisse2012} used optical flow in images captured on board the quadrotor to obtain necessary relative information for control.

\subsection{Planning}
In the literature we reviewed, rendezvous planning was neglected as it was assumed that quadrotor has a clear view of its landing target. Most authors tend to focus on the detection and estimation of the quadrotor's pose relative to the target and maintaining an accurate estimation throughout the landing procedure which is mostly handled by a series of control loops.

\subsection{Control}
A comparison between a PID and Linear Quadratic Control (LQC) was explored in \cite{Friis2009}. However the authors admit, even though LQC performed slightly better than the PID controller the difference was minor and may be attributed to the additional time spent tuning the LQC. In \cite{Herisse2012} a PID controller was developed to land on a oscillating platform in the vertical direction with no lateral movement. While interesting, the solution took over 1 minute to transition from hovering over the landing pad to landing. Additionally the experiments did not seem to account for pitch or roll of the platform.

\section{Methodology}

\section{Hardware}
\subsection{Quadrotor}
For the hardware, we have chosen to reuse equipment that is readily available to us in the Wave Lab. For the quadrotor we have been using the DJI F450 quadrotor frame, Emax 2213-935KV motors with complimentary 1045R propellers, Thunder Power lipo 11.1V 4200mah battery, DJI E310 420S 20A electronic speed controller and Pixhawk v2.4 as our flight controller.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\linewidth]{images/quadrotor.jpg}
	\caption{DJI F450 with Pixhawk v1.5}
\end{figure}

\subsubsection{Onboard Autonomous Control System}
In terms of onboard autonoumos control, we have decided to use the Odriod XU4 due to its size and processing power available, and a Logitech C270 HD webcam as our vision sensor. One problem we may face very soon is the narrow field of view and relatively low frame rate (25Hz) the logitech webcam has. We will be keeping our options open, and plan on replacing the logitech webcam with a Ximia xiQ USB3 camera with a wide angle lens in the near future.

\subsection{Vision Capture}
Firefly camera

\subsubsection{Pixhawk Firmware - PX4}
As mentioned in the hardware section, we have had numerous issues with regards to using the software suite for the Pixhawk Flight Controller, as well as the PX4 firmware itself. There are many instances where we could not explain the instability of the quadrotor during flight, many of which lead to costly crashes, but we believe through these experiences we have developed a procedure to lower the risk for such instances from happening often.

\subsubsection{Odriod to Pixhawk Communication}
For our autonomous system to control the quadrotor directly, the Odriod has to be able to communicate with the Pixhawk, this is where \verb|mavros| (ROS package) comes into play. Mavlink is a popular UAV communication protocol between UAV and ground control softwares, \verb|mavros| creates a mavlink ROS node to enable developers to monitor and issue mavlink commands with ease. We have successfully used mavros to arm and disarm Pixhawk (tested), in the near future we should be able to send velocity/attitude commands to control the quadrotor.

\subsubsection{AprilTag}
On the landing target from we have successfully calibrated the Logitech webcam and used the Apriltag library to obtain a pose estimate, and have manually verified the estimates are accurate, for distance the error is $\pm 1$cm. We have also successfully implemented the ability to identify two different apriltags of different sizes (see Fig~\ref{fig:apriltag}), pose estimates from both apriltags are equal.

Next is to workout how to transform the measurements from the pose estimates of the apriltags in relation to the quadrotor's body frame.

\subsection{Quadrotor Control}
In reviewing prior work, a reoccurring problem lies in the difficulty in maintaining an accurate pose estimation between the quadrotor and the landing target throughout the entire manoeuvre. As the quadrotor approaches the landing target, the target often goes beyond the camera's field of view, causing camera based navigation techniques to fail. Furthermore, in certain conditions the tilt angle of the quadrotor could cause difficulty in maintaining a visual on the landing pad for a downward facing or fixed camera.

To address both of these issues, we propose a novel solution utilizing an nested apriltags which we term inception apriltag. We will replicate the experiment performed by \cite{Ling2014}, where we assume the quadrotor already has a visual of the landing platform. We aim to implement a series of controllers for the approach and landing of the quadrotor to the moving landing platform.

\subsection{Measurement and State Estimation}

One of the major challenges when using AprilTags on a robot that has limited computational power, such as a quadrotor, is the rate at which the AprilTag library can compute the state. This problem is exacerbated when using larger image sizes as the computational time of the AprilTag software appears to grow at least exponentially as shown in (add a figure here). This problem was also noted in the work of \cite{Ling2014} and he addressed the issue by reducing the brightness of the image so that majority of the image is black except for the april tag. An example of this implementation is shown in figure (Kevins image). This allowed Ling \cite{Lee2012} to calculate states at a rate of approximatly 10 - 15 fps but it came at the cost of requiring the brightness parameters to be set ahead of time and also removed a lot of the robustification that is provided in the standard AprilTag library.

@@

\subsection{Adaptive Image Preprocessing}

@@

\section{Results}

>>>>

\section{Introduction}
Over the years there has been been at least some interest in the problem of landing a quadrotor on a moving platform and there have been at least 5 academic publications on the topic \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012}. The problem has been explored from a fairly wide range of approaches.

@@

The autonomous landing problem can be thought of as a set of three separate control problems or stages. First the quadrotor must detect the relative position and velocity of the landing target using either GPS of visual methods. Next the quadrotor must determine a rendezvous location with the landing target and plan the required flight trajectory. Once the quad has rendezvoused a final landing trajectory must be calculated between quadrotor and the landing pad.

In this project we focus developing a set of controllers that produce the final landing trajectory and using a fiducial marker called an AprilTag \textbf{\textit{CITE APRILTAGS}} to provide the estimated state of the quadrotor relative to the landing pad.

\section{Related Work} \textbf{(Needs love but might also just be cut.) }

For perception existing solutions use a variety of simple to complex techniques. In \cite{Kim2014} a basic color threshold technique was to identify the landing target, while \cite{Herisse2012} used optical flow in images captured on board the quadrotor to obtain necessary relative information for control.

A comparison between a PID and Linear Quadratic Control (LQC) was explored in \cite{Friis2009}. However the authors admit, even though LQC performed slightly better than the PID controller the difference was minor and may be attributed to the additional time spent tuning the LQC. In \cite{Herisse2012} a PID controller was developed to land on a oscillating platform in the vertical direction with no lateral movement. While interesting, the solution took over 1 minute to transition from hovering over the landing pad to landing. Additionally the experiments did not seem to account for pitch or roll of the platform.

\section{Methodology}
The majority of effort in this project so far can be separated into two individual but complementary pieces. First, a significant effort effort was spent on ensuring the quadrotor's state was updated a a rate of at least 20 $Hz$. Next, using the information in the state  a set of PID controllers were developed that along with a state machine monitors the current relative position of the quadrotor and either initiates a landing procedure or attempts to minimize the relative displacement and velocity between the quadrotor and the landing pad in the horizonal plane.

\subsection{Measurement and State Estimation using AprilTags}
One of the major challenges when using AprilTags on a robot that has limited computational power, such as a quadrotor, is the rate at which the AprilTag library can compute the state. This problem is exacerbated when using larger image sizes as the computational time of the AprilTag software appears to grow at least exponentially as shown in (add a figure here). This problem was also noted in the work of \cite{Ling2014} and he addressed the issue by reducing the brightness of the image so that majority of the image is black except for the AprilTag. An example of this implementation is shown in figure (Kevins image). This allowed Ling \cite{Lee2012} to calculate states at a rate of approximatly 10 - 15 fps but it came at the cost of requiring the brightness parameters to be set ahead of time and also removed a lot of the robustification that is provided in the standard AprilTag library.

@@

\subsubsection{Adaptive Image Preprocessing}

@@

\subsection{Controller and State Monitoring}

\section{Experimental Hardware}
The quadrotor used in this experiment assembled from a DJI F450 quadrotor frame, 4 Emax 2213-935KV motors with complementary DJI E310 420S 20A electronic speed controllers. The flight controller selected for the project was a Pixhawk v2.4 running the PX4 firmware stack. An Odroid XU4 was selected as the onboard computer to processes captured images from a video stream and sends attitude commands via usb to the Pixhawk based of the PID controllers and current state as outlined above. Communication between the Odroid and the Pixhawk is handled by the mavros package which is a wrapper around the popular Mavlink communication protocal for UAVs.  Video was captured using a PointGrey Firefly 2.0 camera operating 60 frames per second (fps) with a resolution of 640 by 480 pixels along with a FujiFilm 135 degree FOV lens. The quadrotor and camera are highlighted in Figure \ref{Quadrotor}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\linewidth]{images/quadrotor.jpg}
	\caption{DJI F450 with Pixhawk v1.5}
	\label{Quadrotor}
\end{figure}

\section{Results}
\begin{itemize}
	\item Results of the image stuff
	\begin{itemize}
		\item Plot of FPS vs distance
		\item Plot of true state vs mocap state?
	\end{itemize}

	\item PID/Control results 
	\begin{itemize}
		\item Plot XY for the controller loop
		\item Optimal PID settings
		\item How we got there
		\item Decent plot (V as a funtion of Z)
		\item Decent planner
		\item Video?
	\end{itemize}

\end{itemize}
